\documentclass[11pt]{scrartcl}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage[ddmmyyyy]{datetime}
\renewcommand{\dateseparator}{--}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{xcolor}
%\definecolor{cvlinkcolor}{RGB}{6,125,233}
\usepackage{hyperref}
\hypersetup{
    pdfborder={0 0 0},
    breaklinks=true,
    colorlinks=true,
    linkcolor=black,
    citecolor=black,
    urlcolor=black
}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\rhead{\small{Last updated: \today}}
\pagestyle{fancy}

% Custom commands for consistent formatting
\newcommand{\cvsection}[1]{\subsection*{#1}}
\newcommand{\cventry}[3]{\begin{tabularx}{\linewidth}{@{}p{0.15\linewidth}@{\hspace{0.5em}}X@{}}
    #1 & #2 \hfill #3
\end{tabularx}}

\setlength{\emergencystretch}{3em}
\setcounter{secnumdepth}{0}

\begin{document}

{\LARGE \textbf{Ryan Campbell}\hfill}
\hrule height 1pt \vspace{1em}

\begin{tabularx}{\linewidth}{@{}Xr@{}}
    Laboratoire J.A. Dieudonné & Webpage: \url{www.ryanstats.com}\\
    Université Côte d'Azur & Email: \url{ryan.campbell@univ-cotedazur.fr} \\
    Parc Valrose, 28 Avenue Valrose & \\
    06000 Nice, France & 
\end{tabularx}
\vspace{1em}

\cvsection{Research Interests}
Multivariate and spatio-temporal extreme value theory, dependence modelling, applications to real world data.

\cvsection{Professional Activities}
\begin{itemize}[leftmargin=*,nosep]
    \item \textbf{2025--2028} Postdoctoral researcher, Université Côte d'Azur, Nice, France
    \item \textbf{2020--2021} Data science intern, Desjardins General Insurance Group, Lévis, Québec
\end{itemize}

\cvsection{Education}
\begin{itemize}[leftmargin=*,nosep]
    \item \textbf{2021--2025} PhD Statistics, Lancaster University \\
    Thesis: \textit{A geometric interpretation of multivariate extreme value analysis} \\
    Supervisor: Jennifer L. Wadsworth

    \item \textbf{2019--2020} MSc Mathematics \& Statistics, McGill University \\
    Thesis: \textit{Deterministic Gaussian averaged neural networks} \\
    Supervisor: Adam Oberman

    \item \textbf{2015--2018} BSc Mathematics, McGill University \\
    Project: \textit{Semiparametric modelling of max-stable processes using Kendall's tau} \\
    Supervisor: Johanna Nešlehová
\end{itemize}

\cvsection{Publications}

\subsubsection*{Published/To Appear}
\begin{enumerate}[leftmargin=*,nosep]
    \item \textbf{R. Campbell}, K. Grolmusova, L. Kakampakou, and J. Lee. Analysing Extreme Rainfall via a Geometric Framework, \emph{Extremes. To appear. 2026.}
    \item L.M. André, \textbf{R. Campbell}, E. D'Arcy, A. Farrell, D. Healy, L. Kakampakou, C. Murphy, C.J.R. Murphy-Barltrop, M. Speers. Extreme value methods for estimating rare events in Utopia. \emph{Extremes}, 1--23, 2024.
    \item J. L. Wadsworth and \textbf{R. Campbell}. Statistical inference for multivariate extremes via a geometric approach. \emph{Journal of the Royal Statistical Society Series B: Statistical Methodology}, (86)5: 1243--1265, 2024.
\end{enumerate}

\subsubsection*{In Preparation}
\begin{enumerate}[leftmargin=*,nosep]
    \item \textbf{R. Campbell}, E. Di Bernardino, and T. Opitz. Analysis of spatial extreme events via excursion set geometry. \emph{In preparation}, 2026+.
    \item \textbf{R. Campbell} and J. L. Wadsworth. The geometry of standardized multivariate generalized Pareto random vectors. \emph{In preparation}, 2026+.
\end{enumerate}

\subsubsection*{Preprints/Submissions}
\begin{enumerate}[leftmargin=*,nosep]
    \item \textbf{R. Campbell} and J. L. Wadsworth. Piecewise-linear modeling of multivariate geometric extremes. \emph{arXiv:2412.05195}, 2024.
    \item I. Papastathopoulos, L. de Monte, \textbf{R. Campbell}, H. Rue. Statistical inference for radially-stable generalized Pareto distributions and return level-sets in geometric extremes. \emph{arXiv:2310.06130}, 2023.
    \item \textbf{R. Campbell}, C. Finlay, and A. M. Oberman. Adversarial Boot Camp: label free certified robustness in one epoch. \emph{arXiv:2010.02508}, 2020.
    \item \textbf{R. Campbell}, C. Finlay, and A. M. Oberman. Deterministic Gaussian averaged neural networks. \emph{arXiv:2006.06061}, 2020.
\end{enumerate}

\cvsection{Selected Presentations}
\begin{itemize}[leftmargin=*,nosep]
    \item \textbf{June 2026} Extreme events in agriculture and forestry: Challenges, methods, applications \\
    Title: Analysis of extreme spatial dependence using excursion set geometry \\
    Location: Avignon University, Avignon, France

    \item \textbf{June 2026} $57^{\text{es}}$ Journées de Statistique de la Société Française de Statistique \\
    Title: Analysis of extreme spatial dependence using excursion set geometry \\
    Location: Clermont Auvergne University, Clermont-Ferrand, France

    \item \textbf{June 2025} $14^{\text{th}}$ International Conference on Extreme Value Analysis \\
    Title: Geometric spatio-temporal extremes \textit{(with Kristina Grolmusova, Lydia Kakampakou, and Jeongjin Lee)} \\
    Location: University of North Carolina, Chapel Hill, NC, USA

    \item \textbf{June 2025} $14^{\text{th}}$ International Conference on Extreme Value Analysis \\
    Title: Piecewise-linear modeling of multivariate geometric extremes \\
    Location: University of North Carolina, Chapel Hill, NC, USA

    \item \textbf{Nov. 2024} Various statistics seminars in France and Switzerland \\
    Title: A geometric approach to multivariate extremal inference \\
    Locations: Inria Grenoble, Université de Genève, École Polytechnique Fédérale de Lausanne, Université Claude Bernard Lyon 1, INRAE Avignon

    \item \textbf{Sept. 2024} UQÀM Statistics Seminar \\
    Title: New developments for a geometric approach to multivariate extremal inference \\
    Location: UQÀM, Montréal, QC, Canada

    \item \textbf{Oct. 2023} HEC Statistics Seminar \\
    Title: Statistical inference for multivariate extremes via a geometric approach \\
    Location: HEC Montréal, Montréal, QC, Canada

    \item \textbf{Sept. 2023} STOR-i Extremes Workshop (STEW) \\
    Title: Modelling extremal dependence of a 3-dimensional oceanographic dataset via a semi-parametric geometric approach \\
    Location: Lancaster University, Lancaster, UK

    \item \textbf{June 2023} $13^{\text{th}}$ International Conference on Extreme Value Analysis \\
    Title: A geometric approach for modelling negative asymptotic dependence \\
    Location: Bocconi University, Milan, Italy
\end{itemize}

\cvsection{Teaching Assistant Positions}

\subsubsection*{Lancaster University}
\begin{itemize}[leftmargin=*,nosep]
    \item Winter 2024: MATH333 Statistical Models
    \item Winter 2024: MATH113 Convergence and Continuity
    \item Winter 2023: MATH140 Statistics
    \item Winter 2022: MATH456/556 Extreme Value Theory
    \item Winter 2022: MATH235 Statistics II
    \item Fall 2021: MATH330 Likelihood Inference
\end{itemize}

\subsubsection*{McGill University}
\begin{itemize}[leftmargin=*,nosep]
    \item Fall 2020: MATH208 Intro. to Statistical Computing
    \item Fall 2019: MATH597 Topics in Applied Mathematics: Mathematics of Machine Learning
    \item Fall 2019: MATH223 Linear Algebra
\end{itemize}

\cvsection{Awards and Funding}
\begin{itemize}[leftmargin=*,nosep]
    \item 2023--2025: NSERC Postgraduate Scholarship-Doctoral (CA\$63,000)
    \item 2023--2025: FRQNT Doctoral Research Scholarship (CA\$25,334)
    \item 2021--2025: EPSRC Mathematical Sciences studentship (£62,436 minimum)
    \item 2025: London Mathematical Society Early Career Researcher Travel Grant (£500)
    \item 2025: Institute of Mathematics Small Grant (£600)
    \item 2025: Graduate College \& Doctoral Academy Travel Grant, Lancaster University (£200)
    \item 2023: Nick Smith Prize, Lancaster University (£500)
    \item 2020: Mitacs internship at Desjardins (CA\$13,000)
    \item 2019--2020: Master's degree funding (CA\$20,500)
    \item 2019--2020: McGill University Graduate Excellence Award (CA\$3,400)
    \item 2018: Science Undergraduate Research Award (CA\$6,500)
\end{itemize}

\cvsection{Languages and Skills}
\begin{itemize}[leftmargin=*,nosep]
    \item Fluent in English and French
    \item Proficient in R, Python (incl. PyTorch), Matlab, \LaTeX, Java, HTML, Linux
\end{itemize}

\cvsection{Extracurricular Activities}
\begin{itemize}[leftmargin=*,nosep]
    \item \textbf{Treasurer}, Bowland Ultra, Lancaster, UK (2023--2025)
    \item \textbf{Treasurer}, Lancaster University Folk Society (2023--2025 academic years)
    \item \textbf{VP Finance}, Graduate Student Association for Mathematics and Statistics (GSAMS), McGill University (2019--2020 academic year)
    \item \textbf{Volunteer} at the 2018 Statistical Society of Canada annual meeting (3--6 June 2018, McGill University) \\
    Roles: Setting up audio-visual equipment and directing conference attendees
\end{itemize}

\end{document}